---
title: "Kursøvelser for Bibliometri for latsabber"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Hva er dette for noe?

Dette er en interaktiv øvelsessamling til kurset Bibliometri for latsabber. 

### Men...hvorfor?

> Av alle lidenskapar er latskapen den sterkaste, ja, 
> ingen lidenskap er sterkare enn lidenskapen latskap, 
> det er i latskapen sinnet er mest kjenslevart. 
>
> [--- Samuel Beckett, **Ord og tonar**]{style="float:right"}

<br>
<br>
Sagt på en annen måte: kursansvarlig er også lat, og dette må dere gjøre sjøl...


## R og RStudio



### Øvelse 1:  

La oss starte med å bare gjøre oss kjent med å skrive kode.

*Lag en variabel av navnet på din institusjon og tildel den institusjonsnummeret*:

```{r inst_navn, exercise = TRUE, exercise.eval = TRUE}

```

```{r inst_navn-hint}
ntnu <- 194
```


### Øvelse 2: 

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Ryddige data

### Øvelse 3: 

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

## Datasett

### Øvelse 5:

### Øvelse 6:


## Mange kilder

### Øvelse 7:

### Øvelse: 8:


## Visualisering

### Øvelse 9:

### Øvelse 10:


## Rapportering

### Øvelse 11:

### Øvelse 12:
